---
title       : Introduction to R
subtitle    : Slidify
author      : Mohammed Omar
job         : Researcher/Bioinformatician
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap,quiz,interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Slide 2

 
```{r}
library(RColorBrewer)
with(iris, boxplot(Sepal.Length~Species,col=brewer.pal(3,"Set1")))

```

---

## Slide 3

```{r}
library(viridis)
with(iris, boxplot(Petal.Length~Species,col=viridis(3)))

```

--- &radio

## Question 1

What is right R syntax to extract the 4th element in the third couln from a dataframe named df?

1. df[3:4]  
2. _df[3,4]_  
3. df[c(3,4),]  
4. df[4,3]  

*** .explanation 
Because dataframe is 2D 
*** .hint
Remember a dataframe is two-dimensional

--- &interactive

## Interactive console

```{r,opts.label='interactive',results='asis'}
require(rCharts)
hair_eye_male <- subset(as.data.frame(HairEyeColor), Sex == "Male")
n1 <- nPlot(Freq ~ Hair, group = "Eye", data = hair_eye_male, type = "multiBarChart")
n1

```


